Hydra Battles and Cie

### 2021-08-17 doc/hydras.tex
use Alectryon 1.3.1
update the doc; minor change to T1Bridge.v

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, \'Evelyne Contejean, Jéremy Damour,   Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Sylvain Salvati, Alan Schmitt and Théo Zimmermann for their help on the elaboration of this library and  document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.

>>>>

%%% One hypothesis per line 
\makeatletter
\renewcommand{\alectryon@hyps@sep}{\alectryon@nl}
\makeatother

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, \'Evelyne Contejean, Jéremy Damour,   Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Cl\'ement Pit-Claudel, Sylvain Salvati, Alan Schmitt and Théo Zimmermann for their help on the elaboration of this library and  document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.

### 2021-08-17 doc/part-hydras.tex
use Alectryon 1.3.1
update the doc; minor change to T1Bridge.v

\input{movies/snippets/T1/LTOnea}

\begin{Coqanswer}
1 subgoal (ID 738)

  alpha1 : T1
  n : nat
  alpha2 : T1
  H1 : nf (ocons alpha1 n alpha2)
  H2 : lt (ocons alpha1 n alpha2) one
  ============================
  ocons alpha1 n alpha2 = zero
\end{Coqanswer}

\input{movies/snippets/T1/LTOneb}

@@

The Gaia project ~\url{https://github.com/coq-community/gaia} maintains Grimm's  theory of ordinals as part of coq-community on GitHub. Integration
of the present ordinal theory with Gaia, i.e., relating the different notions of ordinals
and transferring relevant results, would be an interesting project.

>>>>

\input{movies/snippets/T1/LTOne}

@@

The Gaia project ~\url{https://github.com/coq-community/gaia} maintains Grimm's  theory of ordinals as part of coq-community on GitHub. Integration
of the present ordinal theory with Gaia, i.e., relating the different notions of ordinals
and transferring relevant results, is an interesting project.
First experiments in that direction are developped in
\href{https://github.com/coq-community/hydra-battles/blob/master/theories/gaia/T1Bridge.v}{theories/gaia/T1Bridge.v}.
